---
title: "Biodiversity and Health Bibliometric Analysis: Topic"
author: "Andy Hong"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document
---
  
```{r global_options, include=FALSE}
## Allow duplicate labels
if(!require(knitr)){install.packages("knitr"); require(knitr)} 
opts_knit$set(knitr.duplicate.label = 'allow')
opts_chunk$set(dev = 'png')
opts_chunk$set(dpi = 300)
```


## 1. Setup and load data

Install packages and set up paths

```{r setup, message=FALSE, echo=FALSE}
## Load packages
#install.packages("bibliometrix", dependencies=TRUE)  

require(bibliometrix)
require(ggplot2)
require(networkD3)
require(scales)
#
```


```{r setup, message=FALSE, echo=FALSE}
show_col(hue_pal()(16))
```


```{r setup, message=FALSE, echo=FALSE}
## Home
setwd("//client/H$/Documents/OneDrive - Newcastle University/Papers/DataDecisions/Review")
#my.path = "//client/H$/Documents/OneDrive - Newcastle University/Papers/DataDecisions/Review"

# Read all the WoS BibTex files in the directory 
wos.data = readFiles( "WOS.ciw")


# Read the Scopus BibTex file in the directory
#scopus.data = readFiles(file.path(my.path, "4-Data/2_second_search/scopus.bib"))

TEMP =   file.path(my.path, "/Output", "temp.csv")

```

Load files and merge different database

```{r}
# --------------------------------------------------------
# Load and clean data 
# --------------------------------------------------------

# combine the rows of each dataframe to make one
# long character vector where each item in the vector
# is a single text file
#wos.data = unlist(wos.list)
#df.wos = bib2df(wos.data, dbsource = "isi")
#df.scopus = bib2df(scopus.data, dbsource = "scopus")
df.wos <- convert2df(wos.data, dbsource="wos",format="plaintext")

# Merge WOS and SCOPUS Data
#df = mergeDbSources(df.wos, remove.duplicated=TRUE)


# Remove function
`%notin%` = Negate(`%in%`)

# Remove anonymous or unknown authors
df = subset(df.wos, AU %notin% c("[ANONYMOUS] A", "NA N"))

# If year is NA, then it's likely most recent articles published online
df$PY[is.na(df$PY)] = "2020"


# Limit data from 2015 to 2019
# time.limit = as.character(seq(2015, 2019))
# M = subset(df, PY %in% time.limit)

M = subset(df, !(PY %in% "2020"))
#M = df

#results = biblioAnalysis(d, sep = ";")


```

convert2df creates a bibliographic data frame with cases corresponding to manuscripts and variables to Field Tag in the original export file.

Data frame columns are named using the standard Clarivate Analytics WoS Field Tag codify. 

The main field tags are:

Field Tag  | Description
---------- | -----------
AU		     | Authors
TI		     | Document Title
SO		     | Publication Name (or Source)
JI		     | ISO Source Abbreviation
DT		     | Document Type
DE		     | Authors' Keywords
ID		     | Keywords associated by SCOPUS or ISI database
AB		     | Abstract
C1		     | Author Address
RP		     | Reprint Address
CR		     | Cited References
TC		     | Times Cited
PY		     | Year
SC		     | Subject Category
UT		     | Unique Article Identifier
DB		     | Bibliographic Database


For a complete list of field tags see http://www.bibliometrix.org/documents/Field_Tags_bibliometrix.pdf


## 2. Descriptive analysis

The first step is to perform a descriptive analysis of the bibliographic data frame. 

```{r}

results = biblioAnalysis(df, sep = ";")

```

The function *biblioAnalysis* returns an object of class "bibliometrix".

An object of class "bibliometrix" is a list containing the following components:

List element       | Description
------------------ | --------------------------------------------
Articles		 | the total number of manuscripts
Authors		   | the authors' frequency distribution
AuthorsFrac	 | the authors' frequency distribution (fractionalized)
FirstAuthors | first author of each manuscript
nAUperPaper	 | the number of authors per manuscript
Appearances |  the number of author appearances
nAuthors		 | the number of authors
AuMultiAuthoredArt | the number of authors of multi-authored articles
MostCitedPapers | the list of manuscripts sorted by citations
Years		     | publication year of each manuscript
FirstAffiliation | the affiliation of the first author
Affiliations | the frequency distribution of affiliations (of all co-authors for each paper)
Aff_frac		 | the fractionalized frequency distribution of affiliations (of all co-authors for each paper)
CO		       | the affiliation country of the first author
Countries		 | the affiliation countries' frequency distribution
CountryCollaboration | the intra-country (SCP) and inter-country (MCP) collaboration indices
TotalCitation | 		 the number of times each manuscript has been cited
TCperYear		 | the yearly average number of times each manuscript has been cited
Sources		   | the frequency distribution of sources (journals, books, etc.)
DE		       | the frequency distribution of authors' keywords
ID		       | the frequency distribution of keywords associated to the manuscript by SCOPUS and Thomson Reuters' ISI Web of Knowledge databases

### Articles per year

The follwing shows some general patterns of the articles. This excludes the year 2020.

```{r}

# Articles per year
x = biblioAnalysis(M)
Tab=table(x$Years)

## inserting missing years
YY=setdiff(seq(min(x$Years, na.rm=TRUE),
               max(x$Years, na.rm=TRUE)),names(Tab))
Y=data.frame(Year=as.numeric(c(names(Tab),YY)),
             Freq=c(as.numeric(Tab),rep(0,length(YY))))
Y=Y[order(Y$Year),]

names(Y)=c("Year","Freq")

g=ggplot(Y, aes(x = Y$Year, y = Y$Freq)) +
  # geom_bar(stat="identity") +
  geom_point(color = '#00BFC4', size=2, shape=15, alpha = .6) +
  geom_line(color = '#00BFC4', alpha = .6) +
  geom_area(fill = '#00BFC4', alpha = .5) +
  labs(x = 'Year'
       , y = 'Articles') +
  scale_x_continuous(breaks= (Y$Year[seq(1,length(Y$Year),by=4)])) +
  theme(text = element_text(color = "#444444")
        ,panel.background = element_rect(fill = '#FFFFFF')
        ,panel.grid.minor = element_line(color = '#EFEFEF')
        ,panel.grid.major = element_line(color = '#EFEFEF')
        ,axis.title = element_text(size = 9, color = '#000000')
        ,axis.title.y = element_text(vjust = 0.5, angle = 0)
        ,axis.title.x = element_text(hjust = 0.5)
        ,axis.text.x = element_text(size = 7)
      
  ) 

plot(g)

```



### Articles per country

The chart below shows the top 10 most productive countries.


```{r}

x = results
k = 10

# Countries
xx=x$CountryCollaboration[1:k,]
xx=xx[order(-(xx$SCP+xx$MCP)),]
xx1=cbind(xx[,1:2],rep("SCP",k))
names(xx1)=c("Country","Freq","Collaboration")
xx2=cbind(xx[,c(1,3)],rep("MCP",k))
names(xx2)=c("Country","Freq","Collaboration")
xx=rbind(xx2,xx1)
xx$Country=factor(xx$Country,levels=xx$Country[1:dim(xx2)[1]])
g=suppressWarnings(ggplot(data=xx, aes(x=xx$Country, y=xx$Freq,fill=xx$Collaboration)) +
                     geom_bar(stat="identity", alpha=0.8) +
                     scale_x_discrete(limits = rev(levels(xx$Country))) +
                     scale_fill_discrete(name="Collaboration",
                     breaks=c("MCP","SCP"),
                     labels=c("Multiple Country Publications", "Single Country Publications"))+
                     # scale_fill_manual(name="Legend" , values=c("#002F80", "#E69F00")) +
                     labs(title = "Highest Publishing Countries", 
                          x = "Countries", 
                          y = "Number of Articles") +
                     theme_minimal() +
                     theme(plot.caption = element_text(size = 9, hjust = 0.5,
                                                       color = "blue", face = "italic")) +
                     theme(legend.position = c(0.77, 0.2)) +
                     theme(legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  colour ="darkgray")) +
                     coord_flip())

plot(g)

```

### Articles per author

The chart below shows the top 10 most productive authors.


```{r}

# Authors
xx=as.data.frame(x$Authors[1:k])
g=ggplot(data=xx, aes(x=.data$AU, y=.data$Freq)) +
  geom_bar(stat="identity", fill='#00BFC4')+
  labs(title="Highest Publishing Authors", x = "Authors")+
  labs(y = "Number of Articles")+
  theme_minimal() +
  coord_flip() + scale_x_discrete(limits = rev(levels(xx$AU)))

plot(g)
  
# write.csv(M, TEMP)

 
```

### Top-Authors’ Productivity over the Time

The function AuthorProdOverTime calculates and plots the authors’ production (in terms of number of publications, and total citations per year) over the time.

Function arguments are: M a bibliographic data frame; k is the number of k Top Authors; graph is a logical. If graph=TRUE, the function plots the author production over time graph.

```{r}
myauthorprod <- function (M, k, graph) 
{
    M$TC = as.numeric(M$TC)
    M$PY = as.numeric(M$PY)
    AU = names(tableTag(M, "AU"))
    k = min(k, length(AU))
    AU = AU[1:k]
    df = data.frame(Author = "NA", year = NA, TI = "NA", 
        SO = "NA", DOI = "NA", TC = NA, TCpY = NA, 
        stringsAsFactors = FALSE)
    Y = as.numeric(substr(Sys.time(), 1, 4))
    if (!("DI" %in% names(M))) {
        M$DI = "NA"
    }
    for (i in 1:length(AU)) {
        ind = which(regexpr(AU[i], M$AU) > -1)
        TCpY = M$TC[ind]/(Y - M$PY[ind] + 1)
        dfAU = data.frame(Author = rep(AU[i], length(ind)), year = M$PY[ind], 
            TI = M$TI[ind], SO = M$SO[ind], DOI = M$DI[ind], 
            TC = M$TC[ind], TCpY = TCpY, stringsAsFactors = TRUE)
        df = rbind(df, dfAU)
    }
    df = df[-1, ]
    df2 <- dplyr::group_by(df, .data$Author, .data$year) %>% 
        dplyr::summarise(freq = length(.data$year), TC = sum(.data$TC), 
            TCpY = sum(.data$TCpY))
    df2 = as.data.frame(df2)
    df2$Author = factor(df2$Author, levels = AU[1:k])
    g <- ggplot(df2, aes(x = df2$Author, y = df2$year, text = paste("Author: ", 
        df2$Author, "\nYear: ", df2$year, "\nN. of Articles: ", 
        df2$freq, "\nTotal Citations per Year: ", round(TCpY, 
            2)))) + geom_point(aes(alpha = df2$TCpY, size = df2$freq), 
        color = "dodgerblue4") + scale_size(range = c(2, 
        6)) + scale_alpha(range = c(0.3, 1)) + scale_y_continuous(breaks = seq(min(df2$year), 
        max(df2$year), by = 2)) + guides(size = guide_legend(order = 1, 
        "N.Articles"), alpha = guide_legend(order = 2, 
        "TC per Year")) + theme(legend.position = "right", 
        text = element_text(color = "#444444"), panel.background = element_rect(fill = "gray97"), 
        panel.grid.minor = element_line(color = "#FFFFFF"), 
        panel.grid.major = element_line(color = "#FFFFFF"), 
        plot.title = element_text(size = 24), axis.title = element_text(size = 14, 
            color = "#555555"), axis.title.y = element_text(vjust = 1, 
            angle = 0, face = "bold"), axis.title.x = element_text(hjust = 0.95, 
            face = "bold"), axis.text.x = element_text(face = "bold"), 
        axis.text.y = element_text(face = "bold")) + labs(title = "Top-Authors' Production over the Time", 
        x = "Author", y = "Year") + geom_line(aes(x = df2$Author, 
        y = df2$year, group = df2$Author), size = 1, color = "firebrick", 
        alpha = 0.3) + scale_x_discrete(limits = rev(levels(df2$Author))) + 
        coord_flip()
    df$DOI = as.character(df$DOI)
    res <- list(dfAU = df2, dfPapersAU = df, graph = g)
    if (isTRUE(graph)) {
        plot(g)
    }
    return(res)
}

#topAU = authorProdOverTime(df, k = 10, graph = TRUE)
topAU = myauthorprod(df, k = 10, graph = TRUE)


```



### Cited references

To obtain the most frequent cited manuscripts:

```{r}

CR = citations(df, field = "article", sep = ";")
data.frame(CR$Cited[1:10])

```

To obtain the most frequent cited first authors:


```{r}
CR = citations(df, field = "author", sep = ";")

CR.table = data.frame(CR$Cited)

# Remove irrelevant authors
CR.table = subset(CR.table, CR %notin% c("ANONYMOUS","R CORE TEAM","R DEVELOPMENT CORE TEAM"))

CR.table[1:10,]



```


## 3. Bibliographic network analysis

### Co-citation Network

```{r}
# Create a co-citation network

NetMatrix = biblioNetwork(df, analysis = "co-citation", 
                           network = "references", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network, Top 30", 
                type = "fruchterman", size=T, remove.multiple=FALSE, 
                labelsize=0.6,edgesize = 5)
```


### Keyword co-occurrences

The keyword analysis was limited to articles published in the last five years (from 2015 to 2019). This limitation was imposed due to technical issues, but the analysis provides valuable information on how different keywords are related to each other.

```{r, fig.width=7, fig.height=7}


# Create keyword co-occurrences network
NetMatrix = biblioNetwork(df, analysis = "co-occurrences", 
                           network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, 
                n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", 
                size=T,edgesize = 5,labelsize=0.7)

```


### Historical thematic mapping


```{r, fig.width=7, fig.height=5}
nexus = thematicEvolution(M, field="ID", years=c(2015), n=500, minFreq=5, stemming = T)
plotThematicEvolution(nexus$Nodes, nexus$Edges)

```

### Editing Sankey Plot
```{r, fig.width=7, fig.height=5}
nexus = thematicEvolution(M, field="ID", years=c(2015), n=500, minFreq=5, stemming = T)



for (i in 1:length(nexus$Nodes$name)){
 if( nexus$Nodes$name[i] == "management--1991-2015" ) 
 { nexus$Nodes$name[i] <- "management"}
 else if ( nexus$Nodes$name[i] == "management--2016-2019" ) 
  { nexus$Nodes$name[i] <- "management"}
  else if ( nexus$Nodes$name[i] == "model--1991-2015" ) 
 { nexus$Nodes$name[i] <- "model"}
  else if ( nexus$Nodes$name[i] == "patterns--1991-2015" ) 
 { nexus$Nodes$name[i] <- "patterns"}
  else if ( nexus$Nodes$name[i] == "patterns--2016-2019" ) 
  { nexus$Nodes$name[i] <- "patterns"}
  else if ( nexus$Nodes$name[i] == "policy--1991-2015" ) 
  { nexus$Nodes$name[i] <- "policy"}
 else if ( nexus$Nodes$name[i] == "risk--1991-2015" ) 
  { nexus$Nodes$name[i] <- "risk"}
 else if ( nexus$Nodes$name[i] == "risk--2016-2019" ) 
  { nexus$Nodes$name[i] <- "risk"}
  else if ( nexus$Nodes$name[i] == "science--1991-2015" ) 
  { nexus$Nodes$name[i] <- "science"}
  else if ( nexus$Nodes$name[i] == "social-science--1991-2015" ) 
  { nexus$Nodes$name[i] <- "social-science"}
  else if ( nexus$Nodes$name[i] == "social-science--2016-2019" ) 
  { nexus$Nodes$name[i] <- "social-science"}
  else if ( nexus$Nodes$name[i] == "space--1991-2015" ) 
  { nexus$Nodes$name[i] <- "space"}
  else if ( nexus$Nodes$name[i] == "space--2016-2019" ) 
  { nexus$Nodes$name[i] <- "space"}
  else if ( nexus$Nodes$name[i] == "behavior--2016-2019" ) 
  { nexus$Nodes$name[i] <- "behaviour"}
  else if ( nexus$Nodes$name[i] == "knowledge--2016-2019" ) 
  { nexus$Nodes$name[i] <- "knowledge"}
  else if ( nexus$Nodes$name[i] == "time--2016-2019" ) 
  { nexus$Nodes$name[i] <- "time"}
}
Nodes = nexus$Nodes
Edges = nexus$Edges
measure = 'inclusion'
min.flow = 0

my_colour <- 'd3.scaleOrdinal() .domain(["management", "model","patterns", "policy", "risk", "science", "social-science", "space", "management", "behaviour", "patterns", "knowledge","risk", "social-science","space", "time"]) .range(["#F8766D", "#DB8E00" , "#AEA200", "#64B200", "#00BD5C", "#00C17A", "#00BADE", "#00A6FF","#F8766D", "#B385FF", "#AEA200","#EF67EB", "#00BD5C","#00BADE", "#00A6FF", "#FF63B6"]);'

#my_colour <- JS("d3.scaleOrdinal(d3.schemeCategory20);")

switch(measure, inclusion = {
        Edges = Edges[-c(4, 5)]
    }, stability = {
        Edges = Edges[-c(3, 4)]
    }, weighted = {
        Edges = Edges[, -c(3, 5)]
    })

    names(Edges)[3] = "weight"
    Edges = Edges[Edges$weight >= min.flow, ]
    Edges$weight = Edges$weight * 100
    
    
    sankeyNetwork(Links = Edges, Nodes = Nodes, Source = "from", Target = "to", NodeID = "name", Value = "weight",
  width = 900, fontFamily = "sans", fontSize = 12, nodeWidth = 30, NodeGroup = "group",  LinkGroup = "group", colourScale = my_colour)
```
